Monitoring forest health using hyperspectral imagery: Does feature selection improve the performance of machine-learning techniques?

### 2021-04-09 docs/00-manuscripts/ieee/ieee-manuscript.tex
remove ALE plots from manuscript

\subsubsection{ALE Plots}

Most ALE plots show a small absolute change in ALE compared to their respective mean effects (= 0) for all chosen features (less than $\pm 0.001$) (\autoref{fig:fi-hr-ale}).
Also, a medium-to-high relative dynamic over the respective reflectance value range of each variable was observed.

@@

% ALE plots
The ALE plots are hard to interpret because their values are interpreted on a relative scale and differ for each band.
When linking band reflectance values against ALE values of a specific band, a value of 100 has a very different meaning in B67 than in B124 because for the latter, reflectance values of vegetation are naturally higher.
Hence, a reflectance value of 100 would be considered high for B67 but low for B124 with respect to a spectral curve of vegetation.
However, no baseline reflectance value for every feature exists since the absolute reflectance values depend on the sensor characteristics.
ALE plots can be a powerful tool for interpreting feature importance of correlated features but might be limited in their interpretability because only relative comparisons can be conducted.

@@

\section{SVM ALE plots for task HR}

\begin{figure} [ht]
	\begin{center}
		\includegraphics[width=0.48\textwidth] {fi-hr-ale-1.pdf}
		\caption{ALE plots of SVM on dataset HR. The ten most important features from the permutation-based variable importance estimation were used. The y-axis shows the deviation to the mean prediction for each feature, with the mean prediction being centered at zero.}\label{fig:fi-hr-ale}
	\end{center}
\end{figure}

>>>>

@@

@@

% \section{SVM ALE plots for task HR}

% \begin{figure} [ht]
% 	\begin{center}
% 		\includegraphics[width=0.48\textwidth] {fi-hr-ale-1.pdf}
% 		\caption{ALE plots of SVM on dataset HR. The ten most important features from the permutation-based variable importance estimation were used. The y-axis shows the deviation to the mean prediction for each feature, with the mean prediction being centered at zero.}\label{fig:fi-hr-ale}
% 	\end{center}
% \end{figure}
